---
title: "HPDataAnalysis"
author: "Giorgio Cannavacciuolo"
date: '2023-12-12'
output: html_document
---
###Honours Project - Data Analysis

In the present script, I carry out all the data wrangling, preparation, analyses, and visualisations that I have either entirely or partially used for my Investigative Honours Project write-up, focusing on the Theta-Induced Memory Enhancement Effect (TIME), with respect to its longevity, sleep modulation, and the impact of potential peri-encoding confounds. The structure of the script will try to follow the structure of the Results section of the report for clarity. For any questions, please do not hesitate to contact the author of the script and report. 

##Data Preparation
Prior to any analysis, I conduct data preparation steps including loading libraries and data, merging them into a comprehensive dataset, and renaming to enhance clarity.

#Loading libraries needed
```{r}
library(tidyverse)
```

#Loadind Short Delay Memory Data 
```{r}
st1_1 <- read_csv("subj1-block-1-Test.csv")
st1_2 <- read_csv("subj1-block-2-Test.csv")
st2_1 <- read_csv("subj2-block-1-Test.csv")
st2_2 <- read_csv("subj2-block-2-Test.csv")
st3_1 <- read_csv("subj3-block-1-Test.csv")
st3_2 <- read_csv("subj3-block-2-Test.csv")
st4_1 <- read_csv("subj4-block-1-Test.csv")
st4_2 <- read_csv("subj4-block-2-Test.csv")
st5_1 <- read_csv("subj5-block-1-Test.csv")
st5_2 <- read_csv("subj5-block-2-Test.csv")
st6_1 <- read_csv("subj6-block-1-Test.csv")
st6_2 <- read_csv("subj6-block-2-Test.csv")
st7_1 <- read_csv("subj7-block-1-Test.csv")
st7_2 <- read_csv("subj7-block-2-Test.csv")
st8_1 <- read_csv("subj8-block-1-Test copy.csv")
st8_2 <- read_csv("subj8-block-2-Test copy.csv")
st9_1 <- read_csv("subj8-block-1-Test.csv")
st9_2 <- read_csv("subj9-block-2-Test.csv")
st10_1 <- read_csv("subj10-block-1-Test.csv")
st10_2 <- read_csv("subj10-block-2-Test.csv")
st11_1 <- read_csv("subj11-block-1-Test.csv")
st11_2 <- read_csv("subj11-block-2-Test.csv")
st12_1 <- read_csv("subj12-block-1-Test.csv")
st12_2 <- read_csv("subj12-block-2-Test.csv")
st13_1 <- read_csv("subj13-block-1-Test.csv")
st13_2 <- read_csv("subj13-block-2-Test.csv")
st14_1 <- read_csv("subj14-block-1-Test.csv")
st14_2 <- read_csv("subj14-block-2-Test.csv")
st15_1 <- read_csv("subj15-block-1-Test.csv")
st15_2 <- read_csv("subj15-block-2-Test.csv")
st16_1 <- read_csv("subj16-block-1-Test.csv")
st16_2 <- read_csv("subj16-block-2-Test.csv")
st17_1 <- read_csv("subj17-block-1-Test.csv")
st17_2 <- read_csv("subj17-block-2-Test.csv")
st18_1 <- read_csv("subj18-block-1-Test.csv")
st18_2 <- read_csv("subj18-block-2-Test.csv")
st19_1 <- read_csv("subj19-block-1-Test.csv")
st19_2 <- read_csv("subj19-block-2-Test.csv")
st20_1 <- read_csv("subj20-block-1-Test.csv")
st20_2 <- read_csv("subj20-block-2-Test.csv")
st21_1 <- read_csv("subj21-block-1-Test.csv")
st21_2 <- read_csv("subj21-block-2-Test.csv")
st22_1 <- read_csv("subj22-block-1-Test.csv")
st22_2 <- read_csv("subj22-block-2-Test.csv")
```
#Loading Long Delay Memory Data
```{r}
lt1_1 <- read_csv("subj1-block-1-Test.csv")
lt1_2 <- read_csv("subj1-block-2-Test.csv")
lt2_1 <- read_csv("subj2-block-1-Test.csv")
lt2_2 <- read_csv("subj2-block-2-Test.csv")
lt3_1 <- read_csv("subj3-block-1-Test.csv")
lt3_2 <- read_csv("subj3-block-2-Test.csv")
lt4_1 <- read_csv("subj4-block-1-Test.csv")
lt4_2 <- read_csv("subj4-block-2-Test.csv")
lt5_1 <- read_csv("subj5-block-1-Test.csv")
lt5_2 <- read_csv("subj5-block-2-Test.csv")
lt6_1 <- read_csv("subj6-block-1-Test.csv")
lt6_2 <- read_csv("subj6-block-2-Test.csv")
lt7_1 <- read_csv("subj7-block-1-Test.csv")
lt7_2 <- read_csv("subj7-block-2-Test.csv")
lt8_1 <- read_csv("subj8-block-1-Test.csv")
lt8_2 <- read_csv("subj8-block-2-Test.csv")
lt9_1 <- read_csv("subj8-block-1-Test.csv")
lt9_2 <- read_csv("subj9-block-2-Test.csv")
lt10_1 <- read_csv("subj10-block-1-Test.csv")
lt10_2 <- read_csv("subj10-block-2-Test.csv")
lt11_1 <- read_csv("subj11-block-1-Test.csv")
lt11_2 <- read_csv("subj11-block-2-Test.csv")
lt12_1 <- read_csv("subj12-block-1-Test.csv")
lt12_2 <- read_csv("subj12-block-2-Test.csv")
lt13_1 <- read_csv("subj13-block-1-Test.csv")
lt13_2 <- read_csv("subj13-block-2-Test.csv")
lt14_1 <- read_csv("subj14-block-1-Test.csv")
lt14_2 <- read_csv("subj14-block-2-Test.csv")
lt15_1 <- read_csv("subj15-block-1-Test.csv")
lt15_2 <- read_csv("subj15-block-2-Test.csv")
lt16_1 <- read_csv("subj16-block-1-Test.csv")
lt16_2 <- read_csv("subj16-block-2-Test.csv")
lt17_1 <- read_csv("subj17-block-1-Test.csv")
lt17_2 <- read_csv("subj17-block-2-Test.csv")
lt18_1 <- read_csv("subj18-block-1-Test.csv")
lt18_2 <- read_csv("subj18-block-2-Test.csv")
```
#Loading sleep results for short and long
```{r}
sleep_short <- read_csv("Sleep_short.csv")
sleep_long <- read_csv("Sleep_long.csv")
```
#Merging all short delay memory data into one dataset
```{r}
st <- rbind(st1_1, st1_2, st2_1, st2_2, st3_1, st3_2, st4_1, st4_2, st5_1, st5_2, st6_1, st6_2, st7_1, st7_2, st8_1, st8_2, st9_1, st9_2, st10_1, st10_2, st11_1, st11_2, st12_1, st12_2, st13_1, st13_2, st14_1, st14_2, st15_1, st15_2, st16_1, st16_2, st17_1, st17_2, st18_1, st18_2, st19_1, st19_2, st20_1, st20_2, st21_1, st21_2, st22_1, st22_2)

st$delay <- "short"
```
#Merging all long delay memory data into one dataset
```{r}
lt <- rbind(lt1_1, lt1_2, lt2_1, lt2_2, lt3_1, lt3_2, lt4_1, lt4_2, lt5_1, lt5_2, lt6_1, lt6_2, lt7_1, lt7_2, lt9_1, lt9_2, lt10_1, lt10_2, lt11_1, lt11_2, lt12_1, lt12_2, lt13_1, lt13_2, lt14_1, lt14_2, lt15_1, lt15_2, lt16_1, lt16_2, lt17_1, lt17_2, lt18_1, lt18_2)

lt$delay <- "long"
```
#Renaming column headings for clarity in st and lt 
```{r}
st <- st %>% rename(phase_word = `testrespMat_ 6`, phase = `testrespMat_ 8`, response = testrespMat_14, correct = testrespMat_15, participant = `testrespMat_ 1`)
```

```{r}
lt <- lt %>% rename(phase_word = `testrespMat_ 6`, phase = `testrespMat_ 8`, response = testrespMat_14, correct = testrespMat_15, participant = `testrespMat_ 1`)
```

------------------------------------------------

##Data wrangling
Here, I start rearranging the data to match my testing aims, hence computing the number of correct trials (recall accuracy) based on our initial data.

#Creating a column for correct responses in short and long delay memory
```{r}
st <- st %>% mutate(correct_response = (response == correct))
```

```{r}
lt <- lt %>% mutate(correct_response = (response == correct))
```

#Counting right answers for each participant and each phase offset (short & long)
```{r}
correct_counts_st <- st %>% group_by(participant, phase_word, phase, delay) %>%
  summarise(correct_responses = sum(correct_response == TRUE, na.rm = TRUE))
correct_counts_st <- correct_counts_st %>% mutate(correctpercentage = ((correct_responses/16)))

correct_counts_lt <- lt %>% group_by(participant, phase_word, phase, delay) %>%
  summarise(correct_responses = sum(correct_response == TRUE, na.rm = TRUE))
correct_counts_lt <- correct_counts_lt %>% mutate(correctpercentage = ((correct_responses/16)))
```
#Merging together short and long delay for memory and sleep
```{r}
general <- rbind(correct_counts_lt, correct_counts_st)
```

```{r}
sleep <- rbind(sleep_long, sleep_short)
colnames(sleep)[colnames(sleep) == "Participant"] <- "participant"
colnames(sleep)[colnames(sleep) == "Delay"] <- "delay"
```

```{r}
general_sleep <- merge(general, sleep, by = c("participant", "delay"))
```

----------------------------------------

Now that the data are ready, we can proceed with the Results structure.

##Section 3.1 - Assumption Check

#Data preparation and Assumptions Check
```{r}
st_0 <- correct_counts_st %>% filter(phase_word == 'zero')
st_180 <- correct_counts_st %>% filter(phase_word == 'oneeighty')
hist(correct_counts_st$correctpercentage) #Included in Appendix
shapiro.test(correct_counts_st$correctpercentage)

```

```{r}
lt_0 <- correct_counts_lt %>% filter(phase_word == 'zero')
lt_180 <- correct_counts_lt %>% filter(phase_word == 'oneeighty')
hist(correct_counts_lt$correctpercentage) #Included in Appendix
shapiro.test(correct_counts_lt$correctpercentage)
```

##Section 3.2 and 3.3 - The TIME effect replication in short delay recall + The TIME effect longevity across 24 hours

#Descriptive Statistics

#Descriptives - by phase and delay (Table 2)
```{r}
correct_phase_st <- correct_counts_st %>% group_by(phase_word) %>% summarise(mean_correct = mean(correctpercentage), sd_correct = sd(correctpercentage), sem = sd_correct/sqrt(44), min = min(correctpercentage), max = max(correctpercentage))
```

```{r}
correct_phase_lt <- correct_counts_lt %>% group_by(phase_word) %>% summarise(mean_correct = mean(correctpercentage), sd_correct = sd(correctpercentage), sem = sd_correct/36, min = min(correctpercentage), max = max(correctpercentage))
```
```{r}
correct_phase <- rbind(correct_phase_st, correct_phase_lt)
```

```{r}
general_phase <- general %>% group_by(delay, phase) %>% summarise(mean_correct = mean(correctpercentage), sd_correct = sd(correctpercentage))
```

#Inferentials - t-test and 2x2 ANOVA

Aim 1: Paired T-test (phase x recall accuracy in short delay)
```{r}
t_test_st <- t.test(st_0$correctpercentage, st_180$correctpercentage, paired = TRUE)

print(t_test_st)
```

Aim 2: Paired T-test (phase x recall accuracy in long delay)
```{r}
t_test_lt <- t.test(lt_0$correctpercentage, lt_180$correctpercentage, paired = TRUE)

print(t_test_lt)
```

Aim 2.1: 2x2 ANOVA (phase and delay x recall accuracy)
```{r}
anova_phase_delay <- aov(correctpercentage ~ delay * phase_word, data = general)
summary(anova_phase_delay)

posthoc <- TukeyHSD(anova_phase_delay)
print(posthoc)
```

#Visualisation - Figure 4 + alternative visualisations

Computing mean to superimpose
```{r}
mean_data <- general %>%
  group_by(delay, phase) %>%
  summarise(mean_correctpercentage = mean(correctpercentage))
```

General graph with two panels (Figure 4)
```{r}
general_graph <- general %>%
  ggplot(aes(x = factor(phase), y = correctpercentage)) +
  geom_point(alpha = 0.2) +
  geom_line(alpha = 0.2, aes(group = participant)) +
  geom_point(data = mean_data, aes(x = factor(phase), y = mean_correctpercentage), color = "red", size = 3) +
  geom_line(data = mean_data, aes(x = factor(phase), y = mean_correctpercentage, group = 1), color = "red", size = 1) +
  facet_wrap(~delay, labeller = labeller(delay = 
    c("long" = "Long Delay (24h)",
      "short" = "Short Delay (5min)"))) +
  theme_minimal() +
  xlab("Phase offset (degree)") +
  ylab("Accuracy in recall task") +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18, face = "bold"), strip.text = element_text(size = 14)) +
  scale_x_discrete(expand = c(0.1, 0.1))

ggsave("general_graph.png")
```

Alternative, Individual visualisations for st and lt
```{r}
st_graph <- correct_counts %>% ggplot(aes(x = factor(phase), y = correctpercentage, group = participant)) + geom_point(alpha = 0.2) + geom_line(alpha = 0.2) + scale_y_continuous(breaks = seq(0, 1, by = 0.2)) + theme_minimal() + xlab("Phase offset (degree)") + ylab("Accuracy in recall task") + theme(axis.text = element_text(size = 16),  
        axis.title = element_text(size = 18, face = "bold")) + scale_x_discrete(expand = c(0.1, 0.1))

ggsave("st_graph.png")
```
```{r}
lt_graph <- correct_counts_lt %>% ggplot(aes(x = factor(phase), y = correctpercentage, group = participant)) + geom_point(alpha = 0.2) + geom_line(alpha = 0.2) + scale_y_continuous(breaks = seq(0, 1, by = 0.2)) + theme_minimal() + xlab("Phase offset (degree)") + ylab("Accuracy in recall task") + theme(axis.text = element_text(size = 16),  
        axis.title = element_text(size = 18, face = "bold")) + scale_x_discrete(expand = c(0.1, 0.1))
```

##Section 3.4 - The TIME effect and sleep – subjective quality and quantity effects

#Descriptives
```{r}
quantity_descriptives <- general_sleep %>% group_by(delay) %>% summarise(meanquantity = mean(Quantity), sdquantity = sd(Quantity))
```

#Visualisation

Visualising Aim 3
```{r}
general_sleep %>% ggplot(aes(x = phase_word, y = correctpercentage, colour = Quality)) + geom_boxplot() + facet_wrap(~delay)
```
```{r}
general_sleep %>% filter(delay == "short") %>% ggplot(aes(x = phase_word, y = correctpercentage, colour = Quality)) + geom_point() + geom_boxplot()
```
```{r}
general_sleep %>% filter(phase_word == "zero") %>% ggplot(aes(x = Quantity, y = correctpercentage, colour = delay)) + geom_point()
```

```{r}
ggplot(general_sleep, aes(x = Quantity, y = correctpercentage, color = phase_word)) +
  geom_point() + geom_smooth(method = "lm", se = TRUE, aes(group = phase_word)) +
  facet_wrap(~delay) +
  labs(title = "Scatter Plot of Recall Accuracy by Quantity, Faceted by Delay and Phase",
       x = "Quantity", y = "Recall Accuracy")
```

```{r}
ggplot(general_sleep, aes(x = delay, y = correctpercentage, fill = factor(phase_word))) +
  geom_boxplot() +
  facet_grid(. ~ Quality) +
  xlab("Delay") +
  ylab("Correct Percentage") +
  theme_minimal()
```
```{r}
ggplot(general_sleep, aes(x = phase_word, y = correctpercentage, color = factor(factor(Quality)), group = participant)) +
  geom_point(size = 2) + geom_line() +
  facet_grid(. ~ delay) +
  xlab("Qualityy") +
  ylab("Correct Percentage") +
  theme_minimal()
```

```{r}
ggplot(general_sleep, aes(x = phase_word, y = correctpercentage, color = factor(factor(Quantity)), group = participant)) +
  geom_point(size = 2) + geom_line() +
  facet_grid(. ~ delay) +
  xlab("Quantity") +
  ylab("Correct Percentage") +
  theme_minimal()
```

```{r}
ggplot(general_sleep, aes(x = Quantity, y = correctpercentage, color = phase_word)) +
  geom_point(size = 2) + geom_smooth(method = "lm", se = FALSE, aes(group = phase_word)) +
  facet_grid(. ~ delay) +
  xlab("Quantity") +
  ylab("Correct Percentage") +
  theme_minimal()
```

```{r}
general_sleep %>% ggplot(aes(x = Quantity, y = correctpercentage)) + geom_point() + geom_smooth(method = "lm", se = TRUE)
```

#Inferential 
Aim 3.1: 4x2x2 MANOVA (sleep quality, delay, phase x recall accuracy)
```{r}
Sleep_anova <- aov(correctpercentage ~ delay + phase_word + Quality, data = general_sleep)

summary(Sleep_anova)
```

```{r}
tukey_sleep <- TukeyHSD(Sleep_anova)
print(tukey_sleep)
```

```{r}
quantity_model <- lm(correctpercentage ~ Quantity + delay * phase_word, data = general_sleep)


summary(quantity_model)
```

```{r}
quantity_model1 <- lm(correctpercentage ~ Quantity * delay * phase_word, data = general_sleep)

summary(quantity_model1)
```

#Alternative, simpler models for model selection (all non-significant, thus unreported)
```{r}
general_sleep_short <- general_sleep %>% filter(delay == "short")

sleepshortmodel <- lm(correctpercentage ~ Quantity * phase_word, data = general_sleep_short)

summary(sleepshortmodel)
```
```{r}
general_sleep_long <- general_sleep %>% filter(delay == "long")

sleeplongmodel <- lm(correctpercentage ~ Quantity * phase_word, data = general_sleep_long)

summary(sleeplongmodel)
```

##Section 3.5 - 

##Section 3.6 - Chance level performance control
```{r}
# Set the probability of success for a four-option task
probability_of_success <- 1/4

# Number of trials
n <- 16

# Calculate chance level
chance_level <- n * probability_of_success

# Calculate 95% confidence interval for chance level
confidence_interval <- binom.test(chance_level, n, conf.level = 0.95)$conf.int

# Print results
cat("Chance Level:", chance_level, "\n")
cat("95% Confidence Interval:", confidence_interval[1], "-", confidence_interval[2], "\n")

#Find participants who performed at chance level or below
general_filtered <- general %>% filter(correct_responses < 5)
```
#Rerun analyses filtered for participant performing at chance level
```{r}

```

##Section 3.7 - Exploratory Analyses - Emotional confounds analysis
#Data preparation and wrangling
Short Delay Ratings
```{r}
rating_s <- rbind(rating_s1_1, rating_s1_2, rating_s1_3, rating_s1_4, rating_s1_5, rating_s1_6, rating_s1_7, rating_s1_8, rating_s2_1, rating_s2_2, rating_s2_3, rating_s2_3, rating_s2_4, rating_s2_5, rating_s2_6, rating_s2_7, rating_s2_8, rating_s3_1, rating_s3_2, rating_s3_3, rating_s3_4, rating_s3_5, rating_s3_6, rating_s3_7, rating_s3_8, rating_s4_1, rating_s4_2, rating_s4_3, rating_s4_4, rating_s4_5, rating_s4_6, rating_s4_7, rating_s4_8, rating_s5_1, rating_s5_2, rating_s5_3, rating_s5_4, rating_s5_5, rating_s5_6, rating_s5_7, rating_s5_8, rating_s6_1, rating_s6_2, rating_s6_3, rating_s6_4, rating_s6_5, rating_s6_6, rating_s6_7, rating_s6_8, rating_s7_1, rating_s7_2, rating_s7_3, rating_s7_4, rating_s7_5, rating_s7_6, rating_s7_7, rating_s7_8, rating_s8_1, rating_s8_2, rating_s8_3, rating_s8_4, rating_s8_5, rating_s8_6, rating_s8_7, rating_s8_8, rating_s9_1,rating_s9_2, rating_s9_3, rating_s9_4, rating_s9_5, rating_s9_6, rating_s9_7, rating_s9_8, rating_s10_1, rating_s10_2, rating_s10_3, rating_s10_4, rating_s10_5, rating_s10_6, rating_s10_7, rating_s10_8, rating_s11_1, rating_s11_2, rating_s11_3, rating_s11_4, rating_s11_5, rating_s11_6, rating_s11_7, rating_s11_8, rating_s12_1, rating_s12_2, rating_s12_3, rating_s12_4, rating_s12_5, rating_s12_6, rating_s12_7,rating_s12_8, rating_s13_1, rating_s13_2, rating_s13_3, rating_s13_4, rating_s13_5, rating_s13_6, rating_s13_7, rating_s13_8, rating_s14_1, rating_s14_2, rating_s14_3, rating_s14_4, rating_s14_5, rating_s14_6, rating_s14_7, rating_s14_8, rating_s15_1, rating_s15_2, rating_s15_3, rating_s15_4, rating_s15_5, rating_s15_6, rating_s15_7, rating_s15_8, rating_s16_1, rating_s16_2, rating_s16_3, rating_s16_4, rating_s16_5, rating_s16_6, rating_s16_7, rating_s16_8, rating_s17_1, rating_s17_2, rating_s17_3, rating_s17_4, rating_s17_5, rating_s17_6, rating_s17_7, rating_s17_8, rating_s18_1, rating_s18_2, rating_s18_3, rating_s18_4, rating_s18_5, rating_s18_6, rating_s18_7, rating_s18_8, rating_s19_1, rating_s19_2, rating_s19_3, rating_s19_4, rating_s19_5, rating_s19_6, rating_s19_7, rating_s19_8, rating_s20_1, rating_s20_2, rating_s20_3, rating_s20_4, rating_s20_5, rating_s20_6, rating_s20_7, rating_s20_8, rating_s21_1, rating_s21_2, rating_s21_3, rating_s21_4, rating_s21_5, rating_s21_6, rating_s21_7, rating_s21_8, rating_s22_1, rating_s22_2, rating_s22_3, rating_s22_4, rating_s22_5, rating_s22_6, rating_s22_7, rating_s22_8, rating_s23_1, rating_s23_2, rating_s23_3, rating_s23_4, rating_s23_5, rating_s23_6, rating_s23_7, rating_s23_8, rating_s24_1, rating_s24_2, rating_s24_3, rating_s24_4, rating_s24_5, rating_s24_6, rating_s24_7, rating_s24_8)
```

Long Delay Ratings
```{r}
rating_l <- rbind(rating_l1_1, rating_l1_2, rating_l1_3, rating_l1_4, rating_l1_5, rating_l1_6, rating_l1_7, rating_l1_8, rating_l2_1, rating_l2_2, rating_l2_3, rating_l2_3, rating_l2_4, rating_l2_5, rating_l2_6, rating_l2_7, rating_l2_8, rating_l3_1, rating_l3_2, rating_l3_3, rating_l3_4, rating_l3_5, rating_l3_6, rating_l3_7, rating_l3_8, rating_l4_1, rating_l4_2, rating_l4_3, rating_l4_4, rating_l4_5, rating_l4_6, rating_l4_7, rating_l4_8, rating_l5_1, rating_l5_2, rating_l5_3, rating_l5_4, rating_l5_5, rating_l5_6, rating_l5_7, rating_l5_8, rating_l6_1, rating_l6_2, rating_l6_3, rating_l6_4, rating_l6_5, rating_l6_6, rating_l6_7, rating_l6_8, rating_l7_1, rating_l7_2, rating_l7_3, rating_l7_4, rating_l7_5, rating_l7_6, rating_l7_7, rating_l7_8, rating_l9_1,rating_l9_2, rating_l9_3, rating_l9_4, rating_l9_5, rating_l9_6, rating_l9_7, rating_l9_8, rating_l10_1, rating_l10_2, rating_l10_3, rating_l10_4, rating_l10_5, rating_l10_6, rating_l10_7, rating_l10_8, rating_l11_1, rating_l11_2, rating_l11_3, rating_l11_4, rating_l11_5, rating_l11_6, rating_l11_7, rating_l11_8, rating_l12_1, rating_l12_2, rating_l12_3, rating_l12_4, rating_l12_5, rating_l12_6, rating_l12_7,rating_l12_8, rating_l13_1, rating_l13_2, rating_l13_3, rating_l13_4, rating_l13_5, rating_l13_6, rating_l13_7, rating_l13_8, rating_l14_1, rating_l14_2, rating_l14_3, rating_l14_4, rating_l14_5, rating_l14_6, rating_l14_7, rating_l14_8, rating_l15_1, rating_l15_2, rating_l15_3, rating_l15_4, rating_l15_5, rating_l15_6, rating_l15_7, rating_l15_8, rating_l16_1, rating_l16_2, rating_l16_3, rating_l16_4, rating_l16_5, rating_l16_6, rating_l16_7, rating_l16_8, rating_l17_1, rating_l17_2, rating_l17_3, rating_l17_4, rating_l17_5, rating_l17_6, rating_l17_7, rating_l17_8, rating_l18_1, rating_l18_2, rating_l18_3, rating_l18_4, rating_l18_5, rating_l18_6, rating_l18_7, rating_l18_8, rating_l19_1, rating_l19_2, rating_l19_3, rating_l19_4, rating_l19_5, rating_l19_6, rating_l19_7, rating_l19_8, rating_l20_1, rating_l20_2, rating_l20_3, rating_l20_4, rating_l20_5, rating_l20_6, rating_l20_7, rating_l20_8) 

##rating_l21_1, rating_s21_2, rating_s21_3, rating_s21_4, rating_s21_5, rating_s21_6, rating_s21_7, rating_s21_8, rating_s22_1, rating_s22_2, rating_s22_3, rating_s22_4, rating_s22_5, rating_s22_6, rating_s22_7, rating_s22_8, rating_s23_1, rating_s23_2, rating_s23_3, rating_s23_4, rating_s23_5, rating_s23_6, rating_s23_7, rating_s23_8, rating_s24_1, rating_s24_2, rating_s24_3, rating_s24_4, rating_s24_5, rating_s24_6, rating_s24_7, rating_s24_8
```

```{r}
rating_s$delay <- "short"
rating_l$delay <- "long"
Rating <- rbind(rating_s, rating_l)
Rating <- Rating %>% rename(phase_word = `respMat_ 6`, phase = `respMat_ 8`,  rating = respMat_10, participant = `respMat_ 1`, movie = `respMat_ 5`, sound = `respMat_ 7`)
```

```{r}
st_rating <- st %>% rename(movie = `testrespMat_ 5`, sound = `testrespMat_ 7`)
lt_rating <- lt %>% rename(movie = `testrespMat_ 5`, sound = `testrespMat_ 7`)
st_rating$delay <- "short"
lt_rating$delay <- "long"
total <- rbind(st_rating, lt_rating)

total_desc <- total %>% group_by(movie, sound, phase_word, participant) %>% summarise()

rating_desc <- Rating %>% group_by(participant, movie, sound, phase_word) %>% summarise(mean_rating = mean(rating))

total_rating <- merge(total, rating_desc, by = c("participant", "movie", "sound"))

total_rating1 <- merge(total, Rating, by = c("participant", "movie", "sound"))
```

#Visualisations
```{r}
ggplot(total_rating1, aes(x = rating, fill = factor(correct_response))) +
  geom_bar(position = "dodge", stat = "count") +
  scale_fill_manual(values = c("blue", "red"), name = "Correct Response") +
  labs(title = "Relationship between Rating and Correct Response",
       x = "Rating", y = "Count") +
  theme_minimal() + facet_wrap(~as.factor(phase.x))
```
```{r}
total_rating_tidy <- total_rating1 %>% group_by(participant, rating) %>% summarise(correct_performance = sum(correct_response == TRUE), incorrect_performance = sum(correct_response == FALSE))

rating_tidy <- Rating %>% group_by(participant, movie, sound, delay, phase) %>% summarise(rating = mean(rating))

total_rating1 <- merge(total, rating_tidy, by = c("participant", "movie", "sound")) %>% group_by(participant, rating, phase.x, delay.x) %>% summarise(correct_performance = sum(correct_response == TRUE))
```

```{r}
ggplot(total_rating1, aes(x = rating, y = correct_performance, colour = as.factor(phase.x))) + geom_point() + geom_smooth(method = "lm", se = TRUE) + facet_wrap(~delay.x) + theme_minimal()
```

#Inferential
```{r}
glm_rating <- glm(correct_performance ~ phase.x * rating * delay.x, data = total_rating1)

summary(glm_rating)
```




